An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-16 VLDB2026/main.tex
modify recommmendations
Update main.tex

	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.

@@

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
				\hline
				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\
				\hline
				S8: OOD scenarios & CAPS &WinFilter  \\
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}

@@

	\subsubsection{\textbf{Attribute Filtering}}
	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}. Puck and UNG excel on large-scale datasets (S1). ACORN-1 and UNG achieve fast index construction (S2). UNG performs well on different datasets (S3, S4). In addition, CAPS performs well on hard datasets with high LID (S3), while NHQ and StitchedVamana perform better on easy datasets with low LID (S4).
	Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6). Milvus and Faiss serve as general-purpose solutions (S5). UNG stands out for its high recall, precision, and QPS (S7). CAPS performs well in OOD scenarios (S8).

>>>>

	For range filtering queries, we evaluate 4 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, WIT~\cite{wit_dataset}, and Text2Image. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.

@@

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
				\hline
				S6: Resource-constrained Environments & CAPS, Faiss&Faiss, SeRF \\
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}

@@

	\subsubsection{\textbf{Attribute Filtering}}
	We summarize the applicability of different algorithms across various attribute filtering scenarios in Table~\ref{tab:algo_scenarios}. Puck and UNG excel on large-scale datasets (S1). ACORN-1 and UNG achieve fast index construction (S2). UNG performs well on different datasets (S3, S4). In addition, CAPS performs well on hard datasets with high LID (S3), while NHQ and StitchedVamana perform better on easy datasets with low LID (S4).
	Faiss and CAPS can generate relatively compact indexes with low memory usage, which is suitable for resource-constrained situations (S6). Milvus and Faiss serve as general-purpose solutions (S5). UNG stands out for its higher recall, precision, and QPS, and performs well in the OOD scenario (S7, S8).
	\subsubsection{\textbf{Range Filtering}}
